### 2015-07-12 thesis/thesis/chap4/chap4.tex
changes

\section{Related Work}\label{s:related_work}

Most of the recent work on communities of services are either
user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
model, the strategies available to a web service when facing a new
community are requesting to join the community, accepting the
master's invitation to join the community, or refusing the
invitation to join. The set of strategies for communities are
inviting the web service or refusing the web service's join
request. Based on their capacity, market share and reputation, the
two players have different sets of utilities over the strategy
profiles of the game. The main limits of this game model are: 1)
its consideration of only three quality parameters, while the
other factors are simply ignored; and 2) the non-consideration of
the web services already residing within the community. The game
is only between the community master and the new web service, and
the inputs from all the other members and their influence on the
master's decision are simply ignored. The consideration of those
inputs and this influence factor is a significant issue as
existing web services can lose utility or payoff because of the
new member, which can result in an unhealthy and unstable group.
The problem comes from the fact that the existing members should
collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our thesis.

In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. In this work, it is shown how the gains of these
parties are coupled together using a linear optimization process.
However, the optimization problem in this solution tends to
optimize some parameters considering all web services regardless
of their efficiency and contribution to the community's welfare.
Moreover, there are no clear thresholds for accepting or rejecting
new web services. The solution of the optimization problem could,
for instance, suggest web services already residing within the
community to increase or decrease their capacity to cover up the
weakness of other parties in the system. However, a high
performing web service could deviate anytime it finds itself
unsatisfied within the community instead of adjusting its service
parameters.

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalition game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud infrastructures and hardware technologies, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.

All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
So basically, these solutions generally suffer from high complexity, which makes decision making very hard, even impossible in some cases in a real-time fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance. We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. Therefore, web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available. \\

\noindent \textbf{Web Service Communities}

Here we introduce the related research work regarding the engineering and formation of communities of web services. In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al. defined communities of web services as \emph{Service Containers} that aggregate substitutable web services having the same set of operations and providing common functionalities. They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked just as elementary web services. The \emph{Container} is considered as a manager that is responsible for web service selection upon receiving a request on run-time. The authors have proposed a scoring technique based on non-functional requirements of the request and web service capabilities to dynamically chose the web service to perform the requested task. A similar concept was proposed by Maamar et al. in \cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced web service communities as a collection of web services with a common functionality but different QoS properties. A community manager, upon receiving a request, delegates the request to one of its current members. The choice is based on the performance history and quality metrics of each web service. The authors have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requires aggregation of different types of services to satisfy the user. In the same line of research, Benslimane et al. \cite{Liris-2770} have proposed a multi-layer approach grouping similar web services into communities and having an interface implemented as an abstract web service for accessing the community. The considered layers are: composite, management and community. The interactions among those layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC). However, unlike our work, these proposals only tackle the problem of internal community management from the task execution perspective, but not the problem of community formation and the one of dynamically selecting which community to join and which web service to invite. Moreover, the web services selection process is done centrally by the community manager, while we address the problem more realistically from the distributed angle.

In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
service communities with centralized access across distributed web
services. They have proposed a framework for web service
management, query resolution among communities and a query caching
mechanism executed by the manager to improve the performance of
query resolution process among many distributed communities. The
key idea is to cache previous computed results for answering
future queries. Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web
services. The protocol is centrally executed by the community
manager. This architecture has been further extended in
\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
roles have been distinguished for community members: masters and
slaves. Master web services are community managers that lead
communities and are responsible for membership management. They
can invite and convince slave web services to join the community,
and attract new slave web services to their communities by
awarding them better payoff. Moreover, they can eject some slave
members from the community to improve its overall reputation if
these members are misbehaving or cannot provide the promised QoS.
In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
developed a community as a ``cluster'' that groups Web services
based on a specific area of interest. All web services in a given
community share the same functionality. These communities are
created by \emph{third party community providers} which use the
\emph{community ontology} as a template and define a set of
operations that all web services within a community should
provide. Using semantic analysis on web service operations, web
services either find and join a community with similar
functionality or create a new operation description for a new
community. The authors have described the concept of
\emph{community agents} associated to \emph{community providers}.
A community agent is responsible, among other things, of the
registration of services with the community. An example of a
community that provides health care services to senior citizens
has been used. In this example, a governmental entity is needed to
check the health care standards used by the members before
authorizing them to be part of the community. Such a central
entity is represented by the community agent. Thus, community
agents are playing the role of community managers. In a close work
\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
global planning selection algorithm and a delegation algorithm to
be run when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the same role as the community coordinator or
manager. All these proposals have in common the consideration
of the central entity for community management, which includes the hiring and firing of the community members, while our approach is fully distributed. Moreover, the stability of the community has not been investigated. Another major difference with our work is that the decision making process is only one way and unilateral from the community manager perspective. In our contribution, both participants, namely communities and web services, participate in the decision making process and a joining decision is made only if it is the best option for both players.

>>>>

%\section{Related Work}\label{s:related_work}
%
%Most of the recent work on communities of services are either
%user-centric and focus on user satisfaction
%\cite{Chun02user-centricperformance} or system-centric and focus
%on the whole system throughput, performance and utilization. There
%are many contributions in distributed, grid, cluster and cloud
%services which are system-centric. However, in real world
%environments and applications, both users and service providers
%are self-interested agents, aiming to maximize their own profit.
%In those environments, both parties (users and services) will
%collaborate as long as they are getting more benefits and payoff.
%
%In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
%DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
%mechanisms to help users and services maximize their gain. A
%two-player non-cooperative game between web services and community
%master was introduced in
%\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
%model, the strategies available to a web service when facing a new
%community are requesting to join the community, accepting the
%master's invitation to join the community, or refusing the
%invitation to join. The set of strategies for communities are
%inviting the web service or refusing the web service's join
%request. Based on their capacity, market share and reputation, the
%two players have different sets of utilities over the strategy
%profiles of the game. The main limits of this game model are: 1)
%its consideration of only three quality parameters, while the
%other factors are simply ignored; and 2) the non-consideration of
%the web services already residing within the community. The game
%is only between the community master and the new web service, and
%the inputs from all the other members and their influence on the
%master's decision are simply ignored. The consideration of those
%inputs and this influence factor is a significant issue as
%existing web services can lose utility or payoff because of the
%new member, which can result in an unhealthy and unstable group.
%The problem comes from the fact that the existing members should
%collaborate with the new web services, so probably their
%performance as a group can suffer. Existing members may even
%deviate and try to join other communities if they are unsatisfied.
%Those considerations of forming stable and efficient coalitions
%are the main contributions of our thesis.
%
%In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
%for selecting web services has been proposed. In this approach,
%the authors proposed a web service selection process that the
%community masters can use. The approach considers the efficiency
%of all the three involved parties, namely users, web services and
%communities. In this work, it is shown how the gains of these
%parties are coupled together using a linear optimization process.
%However, the optimization problem in this solution tends to
%optimize some parameters considering all web services regardless
%of their efficiency and contribution to the community's welfare.
%Moreover, there are no clear thresholds for accepting or rejecting
%new web services. The solution of the optimization problem could,
%for instance, suggest web services already residing within the
%community to increase or decrease their capacity to cover up the
%weakness of other parties in the system. However, a high
%performing web service could deviate anytime it finds itself
%unsatisfied within the community instead of adjusting its service
%parameters.
%
%In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
%autonomous web services based on coalition game theory has been
%introduced. The authors have proposed an interesting algorithm to
%reach individually stable coalition partition for web services in
%order to maximize their efficiency. The communities choose new web
%services on the promise that it would benefit the community
%without decreasing any other web service's income. In the proposed
%model, the worth of community is evaluated with high emphasis on
%the availability metric and considering price and cost values
%only. The community structure is based on a coordination chain,
%where a web service is considered as a \emph{primary} web service
%and the community task-distribution method initially invokes the
%primary web service and only if the primary web service is
%unavailable, the method invokes the next backup web services as
%they are ordered in the coordination chain. We believe that this
%coordination chain limits the cooperation power as it introduces a
%sort of hierarchy. However, in pure and open cooperative models,
%such as the one we propose in this paper, active cooperation
%activities engaging simultaneously many agents so that they can
%perform the tasks more efficiently are being used. Moreover, if
%the availability is high, which is the case nowadays with the
%recent advancements in cloud infrastructures and hardware technologies, the
%backup web services will end-up having a very low chance of
%getting jobs, especially the ones further in the chain. This will
%results in a considerable waste of web services capabilities.
%
%All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
%So basically, these solutions generally suffer from high complexity, which makes decision making very hard, even impossible in some cases in a real-time fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance. We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. Therefore, web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available. \\
%
%\noindent \textbf{Web Service Communities}
%
%Here we introduce the related research work regarding the engineering and formation of communities of web services. In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al. defined communities of web services as \emph{Service Containers} that aggregate substitutable web services having the same set of operations and providing common functionalities. They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked just as elementary web services. The \emph{Container} is considered as a manager that is responsible for web service selection upon receiving a request on run-time. The authors have proposed a scoring technique based on non-functional requirements of the request and web service capabilities to dynamically chose the web service to perform the requested task. A similar concept was proposed by Maamar et al. in \cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced web service communities as a collection of web services with a common functionality but different QoS properties. A community manager, upon receiving a request, delegates the request to one of its current members. The choice is based on the performance history and quality metrics of each web service. The authors have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requires aggregation of different types of services to satisfy the user. In the same line of research, Benslimane et al. \cite{Liris-2770} have proposed a multi-layer approach grouping similar web services into communities and having an interface implemented as an abstract web service for accessing the community. The considered layers are: composite, management and community. The interactions among those layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC). However, unlike our work, these proposals only tackle the problem of internal community management from the task execution perspective, but not the problem of community formation and the one of dynamically selecting which community to join and which web service to invite. Moreover, the web services selection process is done centrally by the community manager, while we address the problem more realistically from the distributed angle.
%
%In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
%service communities with centralized access across distributed web
%services. They have proposed a framework for web service
%management, query resolution among communities and a query caching
%mechanism executed by the manager to improve the performance of
%query resolution process among many distributed communities. The
%key idea is to cache previous computed results for answering
%future queries. Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
%then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
%proposed an architecture utilizing \emph{Contract-Net} protocol
%for engineering task distribution within communities of web
%services. The protocol is centrally executed by the community
%manager. This architecture has been further extended in
%\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
%conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
%roles have been distinguished for community members: masters and
%slaves. Master web services are community managers that lead
%communities and are responsible for membership management. They
%can invite and convince slave web services to join the community,
%and attract new slave web services to their communities by
%awarding them better payoff. Moreover, they can eject some slave
%members from the community to improve its overall reputation if
%these members are misbehaving or cannot provide the promised QoS.
%In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
%developed a community as a ``cluster'' that groups Web services
%based on a specific area of interest. All web services in a given
%community share the same functionality. These communities are
%created by \emph{third party community providers} which use the
%\emph{community ontology} as a template and define a set of
%operations that all web services within a community should
%provide. Using semantic analysis on web service operations, web
%services either find and join a community with similar
%functionality or create a new operation description for a new
%community. The authors have described the concept of
%\emph{community agents} associated to \emph{community providers}.
%A community agent is responsible, among other things, of the
%registration of services with the community. An example of a
%community that provides health care services to senior citizens
%has been used. In this example, a governmental entity is needed to
%check the health care standards used by the members before
%authorizing them to be part of the community. Such a central
%entity is represented by the community agent. Thus, community
%agents are playing the role of community managers. In a close work
%\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
%global planning selection algorithm and a delegation algorithm to
%be run when a request to execute an operation is received by the
%community. This needs a central entity to run those algorithms.
%Such entity plays the same role as the community coordinator or
%manager. All these proposals have in common the consideration
%of the central entity for community management, which includes the hiring and firing of the community members, while our approach is fully distributed. Moreover, the stability of the community has not been investigated. Another major difference with our work is that the decision making process is only one way and unilateral from the community manager perspective. In our contribution, both participants, namely communities and web services, participate in the decision making process and a joining decision is made only if it is the best option for both players.
